
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Govind Pimpale} \\ \vspace{1pt}
    \small (408) 508-1229 $|$ \href{mailto:gpimpale29@gmail.com}{\underline{gpimpale29@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/govind-pimpale/}{\underline{linkedin.com/in/govind-pimpale/}} $|$
    \href{https://github.com/wz-ml}{\underline{github.com/pimpale}} $|$
    \href{https://pimpale.github.io}{\underline{pimpale.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Los Angeles}{\hspace{-1in}\textbf{Exp. Grad 2025, Computer Science Engineering}}
      {Bachelor of Science in Computer Science | GPA: 4.0, Tau Beta Pi, Upsilon Pi Epsilon}{}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Javascript, Typescript, HTML/CSS, C\#, SQL } \\
     \textbf{Frameworks}{: Tensorflow, Pytorch, Fast.AI, React, Node.js, Bootstrap, Flask, HuggingFace, MongoDB, Unity} \\
     \textbf{Developer Tools}{: Git, VS Code, Google Cloud Platform (GCP), AWS, PyCharm, Jupyter Notebook, JupyterLab} \\
     \textbf{Libraries}{: Scikit-Learn, NumPy, Pandas, Matplotlib / Seaborn}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Machine Learning Intern}{Jun. 2023 -- Oct. 2023}
      {Consensus NLP}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Boosted \textbf{\href{https://consensus.app}{Consensus Search}}'s query speed by over 80\% without losing performance via knowledge distillation of machine learning (ML) models in the search pipeline.}
        \resumeItem{Improved model performance by re-training old models with emerging techniques (Function-Matching Distillation and Stochastic Weight Averaging).}
        \resumeItem{Fine-tuned Consensus ChatGPT plugin's ability to handle broad question syntax with automated prompt search.}
        \resumeItem{Fixed the Consensus Meter's tendency to agree with common misconceptions.}
        \resumeItem{Built a query expansion model to improve search pipeline performance on questions with inexact wording.}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
      {AI Researcher}{Jun. 2023 -- Present}
      {University of California, Los Angeles, Bolei Zhou Lab}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Wrote four tutorials for \textbf{\href{https://github.com/wz-ml/MetaDrive-Tutorials}{a mathematical introduction to human-friendly reinforcement learning}}.}
        \resumeItem{Built a library of offline Reinforcement Learning (RL) benchmarks on the Metadrive environment.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Bioinformatics Researcher}{Sep. 2022 -- Aug. 2023}
      {University of California, Los Angeles, Orsulic Labs}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Analyzed the relationship between ovarian cancer cell features and cancer progression with large computer vision models and discovered links between risk-factor genes and tumor appearance.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AlphaZero-Connect4} $|$ \emph{Python, Jupyter, Pytorch, Matplotlib, PIL} $|$ \underline{\textbf{\href{https://github.com/wz-ml/A0-Connect4}{Github}}}}{Dec. 2022 -- Jan. 2023}
          \resumeItemListStart
            \resumeItem{Reimplemented the AlphaZero algorithm on Connect-4, which is so far undefeated by humans at AI Safety socials.}
            \resumeItem{Benchmarked AlphaZero against earlier RL algorithms - DQNs, neuro-evolution, and REINFORCE.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Growing Images with Cellular Automata} $|$ \emph{OpenCV, PyTorch} $|$ \href{https://github.com/wz-ml/cellularimages}{\underline{\textbf{Github}}}}{Apr. 2023 -- May. 2023}
          \resumeItemListStart
            \resumeItem{Implemented Neural Cellular Automata trained to produce and regenerate images. Like Conway's Game of Life, the image grows from a single pixel with an RNN as the learned update rule.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Day2Night} $|$ \emph{Python, OpenCV, Keras, Pix2Pix, PIL, Git} $|$ \href{https://github.com/wz-ml/Day2Night-with-Pix2Pix}{\underline{\textbf{Github}}}}{July 2020 -- Oct. 2020}
          \resumeItemListStart
            \resumeItem{Trained a computer vision Pix2Pix model to convert day photos to night photos (and vice versa).}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Activities}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Projects Officer $\vert$ Competitions Track Lead} {Jun. 2023 - Present}
      {ACM AI}{Los Angeles, CA}
      \resumeItemListStart
            \resumeItem{Hosted a 7-week projects track for 30 students to compete in the \href{https://www.kaggle.com/competitions/stanford-ribonanza-rna-folding}{Kaggle Stanford Ribonanza competition}.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Workshops \& Computational Resources Director}{Oct. 2022 – Present}
      {AI Safety at UCLA}{Los Angeles, CA}
      \resumeItemListStart
            \resumeItem{Ran the AI Safety Intro Fellowship, a program to introduce students to the concept of AI alignment and safety.}
            \resumeItem{Organized UCLA's ML for Alignment Bootcamp, a mathematical workshop to deep-dive into Transformers.}
            \resumeItem{Maintained software and access on the research workstation.}
      \resumeItemListEnd

    \resumeSubheading
      {Secretary}{Oct. 2022 – Present}
      {Engineering Society at UCLA (ESUC)}{Los Angeles, CA}
      \resumeItemListStart
            \resumeItem{Hosted UCLA Engineering's 2023 Alumni Coffee Chats and organized the 2023 Spring Engineering Art Gallery.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
    

%-------------------------------------------
\end{document}
